Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist, cultural&nbsp;data&nbsp;analyst, AI&nbsp;&&nbsp;DH&nbsp;instructor </font>

### 2025-01-05 index.Rmd
news and layout

---
title: "Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analyst | AI&nbsp;&&nbsp;DH&nbsp;instructor </font>"
output: 
  html_document: 
    theme: spacelab
    toc: no
    toc_depth: 4  
    toc_float:
      collapsed: no
---

@@

@@

<div class="container-fluid">
<div class="row">
  <div class="col-sm-7">
  <iframe src="news.html" width="100%" height="200" style="border: none;"></iframe>
  </div>
  <!---
  <div class="col-sm-5">
  <a class="twitter-timeline" 
  data-show-screen-name="false" 
  data-lang="en" 
  data-width="399px" 
  data-height="200px" 
  href="https://twitter.com/AndresKarjus?ref_src=twsrc%5Etfw"
  data-chrome="noheader nofooter">
  " "
  </a> 
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
  </div>
  -->
  <IMG SRC="round.jpg" ALIGN="right" BR CLEAR="left" style="margin-left:10px; width: 20%; height: auto;">
</div>

<div class="row">
<div class="col-sm-12">

### What I do  
<div style="text-align: justify; padding-left:1px"> 
I work on **language and culture dynamics**, using large corpora, machine learning & AI, and cognitive experiments. Recently I have been also working on, through various collaborations, on art history and creative industries, and advising collaborative projects between academia and the public and private sectors. I am affiliated as a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, and at the [Estonian Business School](https://www.ebs.ee/en).
I did my PhD at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of the University of Edinburgh, on lexical dynamics and communicative need in language. <br>
I also occasionally do workshops on **R**, stats & data visualization, and **AI**-related things (see [more here](https://datafigure.eu)).

@@

2023

* Andres Karjus. 2023. Machine-assisted mixed methods: augmenting humanities and social sciences with artificial intelligence | [preprint](https://arxiv.org/abs/2309.14379) | [data&code](https://github.com/andreskarjus/MachineAssistedMixedMethods)
* Indrek Ibrus, Andres Karjus, Vejune Zemaityte, Ulrike Rohn, Maximilian Schich. 2023. Quantifying public value creation by public service media using big programming data.  International Journal Of Communication, 17, 24. | [open access](https://ijoc.org/index.php/ijoc/article/view/21035) 
* Juan Guerrero Montero, Andres Karjus, Kenny Smith, Richard A. Blythe. 2023. Reliable identification of selection mechanisms in language change. Corpus Linguistics and Linguistic Theory | [Open access](https://doi.org/10.1515/cllt-2023-0064)
* Andres Karjus and Christine Cuskley. 2023. Evolving Linguistic Divergence on Polarizing Social Media | arXiv [preprint](https://arxiv.org/abs/2309.01659)
* Tillmann Ohm, Mar Canet Solà, Andres Karjus, Maximilian Schich. 2023. Collection Space Navigator: An Interactive Visualization Interface for Multidimensional Datasets. VINCI 2023: Proceedings of the 16th International Symposium on Visual Information Communication and Interaction. | [open access](doi.acm.org?doi=3615522.3615546) | [extended preprint](https://arxiv.org/abs/2305.06809) | [interactive demo](https://collection-space-navigator.github.io/) | [code](https://github.com/Collection-Space-Navigator/CSN)
* Andres Karjus, Mar Canet Solà, Tillmann Ohm, Sebastian Ahnert, Maximilian Schich. 2023. Compression ensembles quantify aesthetic complexity and the evolution of visual art. EPJ Data Science. 12, 21. | [open access](https://doi.org/10.1140/epjds/s13688-023-00397-3) | [code](https://github.com/andreskarjus/compression_ensembles)
* Oiva, Mila, Ksenia Mukhina, Vejune Zemaityte, Tillmann Ohm, Mikhail Tamm, Andres Karjus, Mark Mets, Daniel Chávez Heras Mar Canet Solà, Helena Hanna Juht, Maximilian Schich. 2023. A Framework for the Analysis of Historical Newsreels | [preprint](https://doi.org/10.31235/osf.io/a4xsp)
* Mehmet Burak Yilmaz, Elen Lotman, Andres Karjus, Pia Tikka. 2023. An embodiment of the cinematographer: emotional and perceptual responses to different camera movement techniques. Frontiers Neuroscience | [open access](https://doi.org/10.3389/fnins.2023.1160843) | [data](https://zenodo.org/record/7979713)
* Vejune Zemaityte, Andres Karjus, Ulrike Rohn, Maximilian Schich, Indrek Ibrus. 2023. Quantifying the global film festival circuit: Networks, diversity, and public value creation | [preprint](https://doi.org/10.31235/osf.io/g9w4b) | [code & data](https://andreskarjus.github.io/cinandofestivals)

2022

* Mark Mets, Andres Karjus, Indrek Ibrus, Maximilian Schich. 2023. Automated stance detection in complex topics and small languages: the challenging case of immigration in polarizing news media | [preprint](https://arxiv.org/abs/2305.13047)
* Andres Karjus, Christine Cuskley. 2022. Evolving linguistic divergence in socio-political polarities. Proceedings of the Joint Conference on Language Evolution (JCoLE). | [proceedings pdf](http://www.evolang.org/jcole2022_proceedings/jcole2022_proceedings.pdf)

2021

* Andres Karjus, Richard A. Blythe, Simon Kirby, Tianyu Wang, Kenny Smith. 2021. Conceptual similarity and communicative need shape colexification". [Cognitive Science](https://doi.org/10.1111/cogs.13035) (open access) | [pdf](https://andreskarjus.github.io/papers/Karjus_2021__Conceptual_Similarity_and_Communicative_Need_Shape_Colexification_An_Experimental_Study__Cognitive_Science.pdf) |  [bib](https://andreskarjus.github.io/bib/karjus_2021_cogsci.bib) | [code and data](https://github.com/andreskarjus/colexification_experiment)

2020

@@

2018

@@

#### Conferences & seminars

@@

</div>
</div>
</div>

## R & AI workshops {#workshops}

I also teach workshops as an instructor in the private sector. 
Some of these have been standalone events, some have been part of conferences, summer schools or academic retreats. 
Feel free to get in touch if you are interested in talking about organizing a workshop on anything related to data science and statistics, artificial intelligence, data visualization, R, corpus linguistics, digital humanities, etc. <br>
For more details and contact, head over to [datafigure.eu](https://datafigure.eu)

@@

- My postdoc includes some teaching activities, and I do occasional guest lectures; recently for the Data Science and Digital Humanities programme at the University of Tartu and for the Cultural Data Analytics I and II courses at Tallinn University.

@@

## Other things
### Semi-academic & science popularization stuff
<div style="text-align: justify">

- Wrote an opinion piece in ERR [Novaator](https://novaator.err.ee/1609007981/andres-karjus-tehisintellekt-seab-juba-sel-sugisel-koolid-sundvaliku-ette) on how generative AI will affect education in the near future (16.06.2023)
- Gave a number of interviews on artificial intelligence and education topics in 2023 (in Estonian):
[Kanal2 Õhtu](https://duoplay.ee/5826/ohtu?ep=749),
[Äripäev radio](https://www.aripaev.ee/saated/2023/03/30/tehisintellekt-muudab-taiskasvanute-oppimist-ja-opikogemust), 
[TÜHI Eeter podcast](https://www.levila.ee/raadio/tuhi-eeter/kumb-on-arukam-kas-inimaru-voi-tehisaru), [PostimeesTV](https://haridus.postimees.ee/7722633/ekspert-eetris-andres-karjus-kas-chatgpt-hakkab-mojutama-meie-vaartusi-ja-kaitumist), BFM [Luna TV](https://www.youtube.com/watch?v=cXpNkDgfP7Y),  [Postimees](https://www.postimees.ee/7717736/tehisintellekti-abil-kodutoo-kirjutajaid-on-pea-voimatu-vahele-votta)
- News piece in [Pealinn](https://pealinn.ee/2022/09/29/vaata-millised-ettevotjad-saavad-tanavu-tunnustamise-osaliseks-ja-voidavad-auhinna/) on Tallinn city enterpreneurship prizes 2022, including me & colleagues for our media monitoring AI prototype in collaboration with AS Ekspress Grupp.
- Hosted students at the CUDAN lab via the job shadowing (töövari) programme of the Estonian Tagasi Kooli programme (online April 2021, live in November 2020).
- I helped my supervisor Prof. Kenny Smith carry out a number of linguistics workshops in primary schools around Edinburgh and Lothian, in school years 2018/2019 and 2019/2020.
- Entered [a video](https://www.youtube.com/watch?v=t8InfFEIINc) to Science Magazine's 11th [Dance Your Ph.D contest](https://www.sciencemag.org/projects/dance-your-phd). The idea is to explain your research topic to the general public though interpretive dance. We didn't win but it was a fun one to do!
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.

### Non-academic stuff

@@

### Before the PhD in Edinburgh

In the more distant past, I worked as a teaching assistant in informatics at the University of Tartu (2015-2016), before that studied artificial intelligence and natural language processing at KU Leuven (MSc) and linguistics at the University of Tartu (BA, MA). I was also affiliated 2016-2019 as a (part-time) junior researcher with the University of Tartu [EKKAM](http://ekkam.ut.ee/en/) sociolinguistics group, doing data analysis and agent-based models. 
During my pre-PhD studies I also went on exchanges to the University of Iceland and the University Vienna, attended a dozen-odd academic summer schools, taught Icelandic to art students and Estonian to Norwegian teachers, worked as an assistant at the Estonian Wordnet project, and did internships at CrossLang NV in Belgium and at (the old) Linguistics Departent of the Max Planck Institute for Evolutionary Anthropology in Leipzig. In earlier years, I worked various studenty sort of jobs to support my studies (for a seller of swords, for a seller of cars, for a minder of horses and tourists).
</div>
<br>

@@

<div style="text-align: center; align:center"> 
<br>
<br>
<br>
**Andres Karjus** <br> 
PhD, MA (linguistics), MSc (artificial intelligence)

Research fellow at <a href=https://cudan.tlu.ee>CUDAN Open Lab, Tallinn University</a> <br>
Senior research fellow at <a href=https://www.ebs.ee>Estonian Business School</a> <br>
Instructor at <a href=https://datafigure.eu>Datafigure OÜ</a>

Academic email: andres.karjus --at-- tlu.ee <br>
Business and workshop inquiries: kindly contact via the Datafigure <a href=https://datafigure.eu/contact.html>email</a>   
<br>
<br>
Twitter / X: <a href=https://twitter.com/AndresKarjus>twitter.com/AndresKarjus</a> <br>
Bluesky: <a href=https://bsky.app/profile/andreskarjus.bsky.social>bsky.app/profile/andreskarjus.bsky.social</a> <br>
Mastodon: <a href=https://mastodon.social/@andreskarjus>mastodon.social/@AndresKarjus</a>
<br>
LinkedIn: <a href="https://www.linkedin.com/in/andreskarjus/">www.linkedin.com/in/andreskarjus/</a> <br> 
</div>

>>>>

---
title: "Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist, cultural&nbsp;data&nbsp;analyst, AI&nbsp;&&nbsp;DH&nbsp;instructor </font>"
output: 
  html_document: 
    theme: spacelab
    toc: no
    toc_depth: 4  
    toc_float:
      collapsed: no
---

@@

/* no indent bullets */
ul {
  margin: 0; /* Removes any default margin */
  padding-left: 15px; /* Moves bullets slightly to the left */
  list-style-position: outside; /* Keeps bullets outside the text block */
}

.profilepic {
  float: right; /* Ensures the image is aligned to the right */
  margin: 10px -5px 10px 10px; /* Adds space on all sides except the right */
  width: 15%; /* Set image width to match your preference */
  height: auto; /* Maintain aspect ratio */
  position: relative; /* Ensure proper positioning */
}

/* General styling for thumbnails */
.thumbnail {
  float: right; /* Ensures the image is aligned to the right */
  margin: 10px; /* Adds space between the image and text */
  margin-right: 0px;
  width: 20%; /* Set image width */
  height: auto; /* Maintain aspect ratio */
  transition: transform 0.3s ease, z-index 0.3s ease; /* Smooth scaling effect */
  position: relative;
  cursor: pointer;
  transform-origin: top right; /* Expands to the left */
}

.thumbnail:hover {
  transform: scale(3); /* Expands the image */
  z-index: 10; /* Ensures the image overlaps other elements */
}

/* Disable hover effects on smaller screens */
@media screen and (max-width: 768px) {
  .thumbnail:hover {
    transform: none;
    z-index: auto;
  }
}

@@

<iframe src="news.html" width="100%" height="110" style="border: 1px solid #ccc; border-radius: 4px; box-shadow: 0 4px 6px rgba(0, 0, 0, 0.1);"></iframe>

<br>

<img src="round.jpg" alt="Profile Picture" class="profilepic">

### What I do

<div style="text-align: justify; padding-left:1px">
I work on language and culture dynamics, using large corpora, machine learning & AI, and cognitive experiments. Recently I have been also collaborating on art history and creative industries projects, and advising cross-sector initiatives between academia and the public and private sectors. I am affiliated with Tallinn University as a lecturer in digital humanities and artificial intelligence (and a member of the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab), and with [Estonian Business School](https://www.ebs.ee/en) as senior researcher.
I did my PhD at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of the University of Edinburgh, on lexical dynamics and communicative need in language. <br>
I also occasionally do consulting and workshops on request on **R**, stats & data visualization, and generative **AI** (see [more here](https://datafigure.eu)). 
I was recently granted the title of "Nationally Recognized Science Communicator" (riiklikult tunnustatud teaduse populariseerija) by the Estonian Science Foundation. <br>
<IMG SRC="lilla-valge-taust-2024.png" ALIGN="right" style="margin-left:0px; width: 15%; height: auto;">
<div style="clear: both; margin-top: 10px;"></div>

@@

2024  <a href="https://www.nature.com/articles/s41599-024-02922-9" target="_blank">
    <img class="thumbnail" src="papers/paper_divergence.png" alt="Divergence Paper Thumbnail">
  </a>

* Andres Karjus and Christine Cuskley. 2024. Evolving Linguistic Divergence on Polarizing Social Media | Nature Humanities and Social Sciences Communications [open access](https://doi.org/10.1057/s41599-024-02922-9) 
* Mark Mets, Andres Karjus, Indrek Ibrus, Maximilian Schich. 2023. Automated stance detection in complex topics and small languages: the challenging case of immigration in polarizing news media | PLOS One [open access](https://doi.org/10.1371/journal.pone.0302380)
* Oiva, Mila, Ksenia Mukhina, Vejune Zemaityte, Tillmann Ohm, Mikhail Tamm, Andres Karjus, Mark Mets, Daniel Chávez Heras Mar Canet Solà, Helena Hanna Juht, Maximilian Schich. 2023. A Framework for the Analysis of Historical Newsreels | Nature Humanities and Social Sciences Communications [open access](https://doi.org/10.1057/s41599-024-02886-w)
* Yan Asadchy; Karjus, Andres; Mukhina, Ksenia; Schich, Maximilian. 2024. Perceived gendered self-representation on Tinder using machine learning | Nature Humanities and Social Sciences Communications [open access](https://doi.org/10.1057/s41599-024-03801-z)
* Tillmann Ohm, A Karjus, M Tamm, M Schich. 2024. fruit-SALAD: A Style Aligned Artwork Dataset to reveal similarity perception in image embeddings | [preprint](https://arxiv.org/abs/2406.01278)    <a href="https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0297404" target="_blank">
    <img class="thumbnail" src="papers/paper_cinando.png" alt="Cinando Paper Thumbnail"></a>
* Andres Karjus, Vejune Zemaityte. 2024. Socioeconomic factors of national representation in the global film festival circuit: skewed toward the large and wealthy, but small countries can beat the odds | [preprint](https://arxiv.org/abs/2407.10755)    
* Vejune Zemaityte and Andres Karjus (co-first), Ulrike Rohn, Maximilian Schich, Indrek Ibrus. 2024. Quantifying the global film festival circuit: Networks, diversity, and public value creation | PLOS One [open access](https://doi.org/10.1371/journal.pone.0297404) | [code, data & interactive dashboard](https://andreskarjus.github.io/cinandofestivals)

<br>2023

* Andres Karjus. 2023. Machine-assisted mixed methods: augmenting humanities and social sciences with artificial intelligence | [preprint](https://arxiv.org/abs/2309.14379) (in press)
* Indrek Ibrus, Andres Karjus, Vejune Zemaityte, Ulrike Rohn, Maximilian Schich. 2023. Quantifying public value creation by public service media using big programming data.  International Journal Of Communication, 17, 24. | [open access](https://ijoc.org/index.php/ijoc/article/view/21035) 
* Juan Guerrero Montero, Andres Karjus, Kenny Smith, Richard A. Blythe. 2023. Reliable identification of selection mechanisms in language change. Corpus Linguistics and Linguistic Theory | [Open access](https://doi.org/10.1515/cllt-2023-0064)
* Tillmann Ohm, Mar Canet Solà, Andres Karjus, Maximilian Schich. 2023. Collection Space Navigator: An Interactive Visualization Interface for Multidimensional Datasets. VINCI 2023: Proceedings of the 16th International Symposium on Visual Information Communication and Interaction. | [open access](doi.acm.org?doi=3615522.3615546) | [extended preprint](https://arxiv.org/abs/2305.06809) | [interactive demo](https://collection-space-navigator.github.io/) | [code](https://github.com/Collection-Space-Navigator/CSN)    <a href="https://epjdatascience.springeropen.com/articles/10.1140/epjds/s13688-023-00397-3" target="_blank">
    <img class="thumbnail" src="papers/paper_compression.png" alt="Compression Paper Thumbnail"></a>
* Andres Karjus, Mar Canet Solà, Tillmann Ohm, Sebastian Ahnert, Maximilian Schich. 2023. Compression ensembles quantify aesthetic complexity and the evolution of visual art. EPJ Data Science. 12, 21. | [open access](https://doi.org/10.1140/epjds/s13688-023-00397-3) | [code](https://github.com/andreskarjus/compression_ensembles) 
* Mehmet Burak Yilmaz, Elen Lotman, Andres Karjus, Pia Tikka. 2023. An embodiment of the cinematographer: emotional and perceptual responses to different camera movement techniques. Frontiers Neuroscience | [open access](https://doi.org/10.3389/fnins.2023.1160843) | [data](https://zenodo.org/record/7979713)

<br>2022

* Andres Karjus, Christine Cuskley. 2022. Evolving linguistic divergence in socio-political polarities. Proceedings of the Joint Conference on Language Evolution (JCoLE). | [proceedings pdf](http://www.evolang.org/jcole2022_proceedings/jcole2022_proceedings.pdf)

2021    <a href="https://doi.org/10.1111/cogs.13035" target="_blank"><img class="thumbnail" src="papers/paper_colex.png" alt="Colexification Paper Thumbnail"></a>

* Andres Karjus, Richard A. Blythe, Simon Kirby, Tianyu Wang, Kenny Smith. 2021. Conceptual similarity and communicative need shape colexification. [Cognitive Science](https://doi.org/10.1111/cogs.13035) (open access) |  [bib](https://andreskarjus.github.io/bib/karjus_2021_cogsci.bib) | [code and data](https://github.com/andreskarjus/colexification_experiment)

<br>2020

@@

<br>2018

@@

#### Conferences & seminars (probably not complete list)

- Presentation and workshop at the Meertens Institute on [AI in humanities](https://meertens.knaw.nl/meertens-event/23-24-oktober-2024-lezing-en-workshop-van-andres-karjus-hoe-grote-taalmodellen-ai-kunnen-helpen-bij-onderzoek/)
- Poster at DHNB2024 in Iceland
- Talk at the AI workshop we organized at [Evolang](https://www.changeiskey.org/event/2024-evolang-workshop/) (May 2024)

@@

## Teaching {#workshops}

<br>

**Private sector**

I also teach workshops as an instructor and provide consulting in the private sector. 
These have taken the form of invited workshop and seminars, standalone events, or components of conferences, summer schools or academic retreats.
Feel free to get in touch if you are interested in talking about organizing a workshop on anything related to data science and statistics, digital skills, artificial intelligence, data visualization, R, corpus linguistics, digital humanities, etc. <br>
For more details, pricing and contact, head over to [datafigure.eu](https://datafigure.eu)

@@

My position now includes some teaching activities on digital skills and AI, and I do occasional guest lectures; recently for the Data Science and Digital Humanities programme at the University of Tartu and for the Cultural Data Analytics I and II courses at Tallinn University.

@@

## Popsci & misc
<div style="text-align: justify">

<br>

**Various essays, media appearances and interviews in Estonian media:**

- Was awarded the "Nationally Recognized Science Communicator" (riiklikult tunnustatud teaduse populariseerija) title at the annual Science Popularization prize 2024 of the Estonian Science Foundation | [press](https://www.tlu.ee/ht/uudised/tallinna-ulikooli-teadlased-palvisid-teaduse-populariseerimise-preemia)
- Appeared in [Kultuuristuudio](https://kultuur.err.ee/1609521805/ajaloolane-kaarel-piirimae-usun-et-tehisintellekt-aitab-valenarratiive-vahendada) on ETV2 TV channel
- Appeared in [Raadio2](https://r2.err.ee/1609521341/andres-karjus-mis-asi-on-ai-treenimine) "Päev" radio segment on training AI
- "1 minute science" video segment in [Novaator](https://novaator.err.ee/1609491088/minutiloeng-kuidas-tehisaru-humanitaare-aidata-saab) on using AI and ML in humanities
- An essay with colleagues in [Sirp](https://sirp.ee/s1-artiklid/c21-teadus/tehisintellekt-ja-humanitaarteadused-kes-vajab-keda/) on humanities and AI
- A piece on AI and education, with colleagues in the Estonian culture journal [Sirp](https://www.sirp.ee/s1-artiklid/c21-teadus/millest-me-raagime-kui-raagime-tehisintellektist-hariduses)
- Wrote an opinion piece in ERR [Novaator](https://novaator.err.ee/1609007981/andres-karjus-tehisintellekt-seab-juba-sel-sugisel-koolid-sundvaliku-ette) on how generative AI will affect education in the near future (16.06.2023)
- Gave a number of interviews on artificial intelligence and education topics in 2023 (in Estonian):
[Kanal2 Õhtu](https://duoplay.ee/5826/ohtu?ep=749),
[Äripäev radio](https://www.aripaev.ee/saated/2023/03/30/tehisintellekt-muudab-taiskasvanute-oppimist-ja-opikogemust), 
[TÜHI Eeter podcast](https://www.levila.ee/raadio/tuhi-eeter/kumb-on-arukam-kas-inimaru-voi-tehisaru), [PostimeesTV](https://haridus.postimees.ee/7722633/ekspert-eetris-andres-karjus-kas-chatgpt-hakkab-mojutama-meie-vaartusi-ja-kaitumist), BFM [Luna TV](https://www.youtube.com/watch?v=cXpNkDgfP7Y),  [Postimees](https://www.postimees.ee/7717736/tehisintellekti-abil-kodutoo-kirjutajaid-on-pea-voimatu-vahele-votta)
- News piece in [Pealinn](https://pealinn.ee/2022/09/29/vaata-millised-ettevotjad-saavad-tanavu-tunnustamise-osaliseks-ja-voidavad-auhinna/) on Tallinn city enterpreneurship prizes 2022, including me & colleagues for our media monitoring AI prototype in collaboration with AS Ekspress Grupp.
- Hosted students at the CUDAN lab via the job shadowing (töövari) programme of the Estonian Tagasi Kooli programme (online April 2021, live in November 2020).
- I helped my supervisor Prof. Kenny Smith carry out a number of linguistics workshops in primary schools around Edinburgh and Lothian, in school years 2018/2019 and 2019/2020.
- Entered [a video](https://www.youtube.com/watch?v=t8InfFEIINc) to Science Magazine's 11th [Dance Your Ph.D contest](https://www.sciencemag.org/projects/dance-your-phd). The idea is to explain your research topic to the general public though interpretive dance. We didn't win but it was a fun one to do!
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.

**Non-academic stuff**

@@

**Before the PhD in Edinburgh**

In the more distant past, I worked as a teaching assistant in informatics at the University of Tartu (2015-2016), before that studied artificial intelligence and natural language processing at KU Leuven (MSc) and linguistics at the University of Tartu (BA, MA). I was also affiliated 2016-2019 as a (part-time) junior researcher with the University of Tartu EKKAM sociolinguistics group, doing data analysis and agent-based models. 
During my pre-PhD studies I also went on exchanges to the University of Iceland and the University Vienna, attended a dozen-odd academic summer schools, taught Icelandic to art students and Estonian to Norwegian teachers, worked as an assistant at the Estonian Wordnet project, and did internships at CrossLang NV in Belgium and at (the old) Linguistics Departent of the Max Planck Institute for Evolutionary Anthropology in Leipzig. In earlier years, I worked various studenty sort of jobs to support my studies (for a seller of swords, for a seller of cars, for a minder of horses and tourists).
</div>
<br>

@@

<div style="text-align: center; align:center"> 
<br>
**Andres Karjus** <br><br>
PhD, MA (linguistics), MSc (artificial intelligence)

Lecturer in digital humanities and AI at Tallinn University <br>
Senior research fellow at Estonian Business School <br>
Instructor at <a href=https://datafigure.eu>Datafigure OÜ</a>

Academic email: andres.karjus --at-- tlu.ee <br>
Business and workshop inquiries: kindly contact via the Datafigure <a href=https://datafigure.eu/contact.html>email</a>   
<br>
<br>
Bluesky: <a href=https://bsky.app/profile/andreskarjus.bsky.social>bsky.app/profile/andreskarjus.bsky.social</a> <br>
Twitter (never calling it X) <a href=https://twitter.com/AndresKarjus>twitter.com/AndresKarjus</a> <br>
Mastodon: <a href=https://mastodon.social/@andreskarjus>mastodon.social/@AndresKarjus</a>
<br>
LinkedIn: <a href="https://www.linkedin.com/in/andreskarjus/">www.linkedin.com/in/andreskarjus/</a> <br> 
</div>

### 2025-01-05 news.Rmd
news and layout

---
title: ''
output: html_document
theme: spacelab
---
<head>
<base target="_blank">
</head>
<style>
.main-container {
  padding: 0px;
}
ul{
  padding-left: 16px;
}
</style>

<div style="width: 100%; padding-top:2px; padding-left:0px; indent-left:0px">

>>>>

---
title: ''
output: html_document
theme: spacelab
---
<head>
<base target="_blank">
</head>
<style>
.main-container {
  padding: 0px;
}
ul {
  margin: 0; /* Removes any default margin */
  padding-left: 15px; /* Moves bullets slightly to the left */
  list-style-position: outside; /* Keeps bullets outside the text block */
  line-height: 1.1; /* Reduces the space between lines */
}

</style>

<div style="width: 100%; padding:0px; indent-left:0px">

- 2024: managed to publish 5 papers (3 preprints still in press) and present in a handful of very nice conferences.
- Mentored at the EdTech 2024 in Tallinn again. Also numerous AI workshops in Estonian schools this year.
- Got awarded the Nationally recognized science communicator quality mark at this year's [awards](https://etag.ee/eesti-teaduse-populariseerimise-elutoopreemia-palvis-toivo-maimets/)
- Visited and gave talks at the Meertens Institute and ILLC in Amsterdam
- Visited the DISSINET group in Brno to discuss applications of AI to historical data
- Appointed lecturer in DH and AI at Tallinn University (September 2024)
- Gave a workshop at the Baltic DH summer school 2024 in Riga again
